Using statistics to guide response to the HIV epidemic

### 2023-05-16 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Upload HiMed draft for review #144

```{r echo=FALSE}
data.frame(
  price = 10,
  effectiveness = 40,
  name = "Condoms"
) %>%
  ggplot(aes(x = price, y = effectiveness, label = name)) +
    geom_text() +
    labs(x = "Price", y = "Effectiveness", title = "Not all interventions can* be provided to everyone", caption = "*Or should") +
    scale_x_continuous(breaks = c(10, 90), labels = c("Cheap", "Expensive"), limits = c(0, 100)) +
    scale_y_continuous(breaks = c(10, 90), labels = c("Works poorly", "Works well"), limits = c(0, 100)) +
    theme_minimal() +
    theme(
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "grey92", linewidth = 0.5, arrow = arrow(length = unit(5, "pt"), type = "open"))
    )
```

>>>>

```{r echo=FALSE}
data.frame(
  price = c(20, 50, 50, 80, 70, 70, 50),
  effectiveness = c(80, 50, 60, 60, 50, 30, 40),
  name = c("Condoms and lube", "STI screening", "Male partner testing", "Access to PrEP", "Access to PEP", "Cash transfers and incentives", "Keep girls in school")
) %>%
  ggplot(aes(x = price, y = effectiveness, label = name)) +
    geom_text() +
    labs(x = "Price", y = "Effectiveness", title = "Not all interventions can, or should, be provided to everyone", caption = "Possible interventions for reducing HIV incidence in AGYW. Positions on plot depend\n on setting, and is subject to uncertainty, so should not be interpreted too precisely.") +
    scale_x_continuous(breaks = c(10, 90), labels = c("Cheap", "Expensive"), limits = c(0, 100)) +
    scale_y_continuous(breaks = c(10, 90), labels = c("Works poorly", "Works well"), limits = c(0, 100)) +
    theme_minimal() +
    theme(
      panel.border = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "grey92", linewidth = 0.5, arrow = arrow(length = unit(5, "pt"), type = "open"))
    )
```
